Predicting sales of newly published books

### 2015-10-30 paper.tex
fixing&improving the text, tanking into account some comments (thanks)
fixing a detail

Obtained results (time to build the model and error) using the different 
forecasting methods on the dataset \textbf{with X variables} per book (obtained 
using the SOM analysis) can be shown in Table \ref{tabla:resultsSOM}.
%In this dataset, every book is described using numerical variables, and thus, 
%processing the data to build the different models is a fast task.
%***************************************
% TODO: falta rellenar la tabla, una vez que hagamos el análisis con el SOM y decidamos qué variables incluir en este dataset
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%) & RRSE (\%)      \\
\hline
  M5P     & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  LR      & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  SVM     & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  kNN     & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  MLP     & x $\pm$ y   & x $\pm$ y & x $\pm$ y  & x $\pm$ y  & x $\pm$ y   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset obtained after the SOM analysis.}}
\label{tabla:resultsSOM}
\end{table*}

Obtained results (time to build the model and error) using the different 
forecasting methods on the dataset with 9 variables per book (obtained 
using the ReliefFAttributeEval feature selection method) can be shown 
in Table \ref{tabla:results9}.
In this dataset, every book is described using numerical variables, and thus, 
processing the data to build the different models is a fast task.

@@

\begin{figure}[!h] 
\begin{center}
  \epsfig{file=fig_time.eps,width=11cm}
\caption{\small{Running time in seconds, obtained after applying the five methods to the reduced datasets (16, 9, 4 and X features each one). Plot shows that using categorical variables as part of the dataset makes the problem hard to solve. As was expected, simpler methods are much faster to build the model than the complex ones.}}
\label{fig:time}
\end{center}
\end{figure}

>>>>

Obtained results (time to build the model and error) using the different 
forecasting methods on the dataset with 7 variables per book (obtained 
using the SOM analysis) can be shown in Table \ref{tabla:resultsSOM}.
%In this dataset, every book is described using numerical variables, and thus, 
%processing the data to build the different models is a fast task.
%***************************************
% TODO: falta rellenar la tabla, una vez que hagamos el análisis con el SOM y decidamos qué variables incluir en este dataset
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%) & RRSE (\%)      \\
\hline
  M5P     & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  LR      & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  SVM     & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  kNN     & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  MLP     & x $\pm$ y   & x $\pm$ y & x $\pm$ y  & x $\pm$ y  & x $\pm$ y   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset obtained after the SOM analysis.}}
\label{tabla:resultsSOM}
\end{table*}

Obtained results (time to build the model and error) using the different 
forecasting methods on the dataset with 8 variables per book (obtained 
using the ReliefFAttributeEval feature selection method) can be shown 
in Table \ref{tabla:results9}.
In this dataset, every book is described using numerical variables, and thus, 
processing the data to build the different models is a fast task.

@@

\begin{figure}[!h] 
\begin{center}
  \epsfig{file=fig_time.eps,width=11cm}
\caption{\small{Running time in seconds, obtained after applying the five methods to the reduced datasets (16, 9, 4 and X features each one). Plot shows that using categorical variables as part of the dataset makes the problem hard to solve. As expected, simpler methods are much faster to build the model than the complex ones.}}
\label{fig:time}
\end{center}
\end{figure}
